Top Text

### 2022-12-11 Paper.tex
commit

\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package

@@

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photorealistic results without having to fine tune any settings apart from the prompt.

@@

	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application. These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance. The closer to zero the distance is, the closer the images are together. zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.

@@

	\section{Results}

	\newpage

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
		\caption{}
		\label{fig:linegraphstablediff}
	\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{Bargraph}
	\caption{}
	\label{fig:bargraph}
\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphDall-E}
		\caption{}
		\label{fig:linegraphdall-e}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphDBW}
		\caption{}
		\label{fig:linegraphdbw}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphMidJ}
		\caption{}
		\label{fig:linegraphmidj}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{boxplotWithAllData}
		\caption{}
		\label{fig:boxplotwithalldata}
	\end{figure}

	\section{Discussion}

>>>>

\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package
\usepackage[section]{placeins}
\usepackage{placeins}

@@

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photo-realistic results without having to fine tune any settings apart from the prompt.

@@

	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application. These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance. The closer to zero the distance is, the closer the images are together. zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.

@@

	\pagebreak
	\section{Results}

	\begin{figure}[!!htbp]
		\centering
		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
		\caption{}
		\label{fig:linegraphstablediff}
	\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{LineGraphMidJ}
	\caption{}
	\label{fig:linegraphmidj}
\end{figure}

\subsection{figure 2 and 3}

What is interesting in both figure one and two is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested. This is seen with Subject two having nearly double the amount of iterations when compared to Subject one in figure one and then Subject 1 having more iterations than Subject two in figure two. Another point of interest is that the application in figure one has as a small amount of iterations when compared to the other applications.  (-make reference to the fact that subject 2 has a bit of exper with sd and subject 1 has expr with midJ-).

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{LineGraphDall-E}
	\caption{}
	\label{fig:linegraphdall-e}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{LineGraphDBW}
	\caption{}
	\label{fig:linegraphdbw}
\end{figure}
\subsection{figure 4 and 5}

In figure two we see it has the most iterations out of any of the other applications. The spread of the distances is also the largest out of any of the other applications. When comparing the amount of iterations that each subject has in both figure on and figure two, these two applications are very close.(-This can be attributed to the fact that the amount of experience with these graphs is very similar for both subjects-)

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{Bargraph}
	\caption{}
	\label{fig:bargraph}
\end{figure}
\subsection{figure 6}
Figure 5 shows that the average distances of all the applications from broth subjects one and two are very close.(this is due to the random nature of t-i-g and shows that a good application is more judged by the functionality it offers rather than its algorithm when it comes to new comers). When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.

	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=1\linewidth]{boxplotWithAllData}
		\caption{}
		\label{fig:boxplotwithalldata}
	\end{figure}
\subsection{figure 7}

	In Figure 6 there are two important points of interest. Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between q2 and q3. Second is that Stable Diffusion has the largest median distance. Mention something about the outliers.

	\pagebreak
	\section{Discussion}
	\subsection{Title}

	During the course of this research we were able to prove the legitimacy of our secondary research question. This was done by a analysing figures two through to six. The applications shown in figure two and three are applications that both subjects have experience in(Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion). What makes figure two and three important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate.

	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in. using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.

	When we take a look at figure six we can see that even though even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars in very small. This can be attributed to the nature of text-to-image generation being that of a random series of attempt until the user reaches a point where they are happy with the picture. This is further proven when you look at any of the patterns for figures 2 through 5 and how the distance for each iterations follows no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.

	\subsection{Secondary research question justification}

	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications. What we do know is that if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make the faster you are more likely to get the result you are looking for.
